Foundations for Inference

### 2018-10-19 DATA606/Foundations for Inference.Rmd
Additional work on homework

(d) Sketch the two distributions (population and sampling) on the same scale.

@@

Suppose you conduct a hypothesis test based on a sample where the sample size is n = 50, and arrive at a p-value of 0.08. You then refer back to your notes and discover that you made a careless mistake, the sample size should have been n = 500. Will your p-value increase, decrease, or stay the same? Explain.

>>>>

```{r}
n <- 15
se <- sd / sqrt(n)
1 - pnorm(x, mu, se)
```

(d) Sketch the two distributions (population and sampling) on the same scale.
```{r, echo=FALSE}
library(ggplot2)
set.seed(4)
pop <- rnorm(1000000, mu, sd)
sample_pop <- sample(pop, 15)
data <-  rbind(data.frame(x=pop, Distribution=c('Population')), data.frame(x=sample_pop, Distribution=c('Sampling')))

ggplot(data, aes(x=x,color=Distribution)) + geom_density()
```

@@

Suppose you conduct a hypothesis test based on a sample where the sample size is n = 50, and arrive at a p-value of 0.08. You then refer back to your notes and discover that you made a careless mistake, the sample size should have been n = 500. Will your p-value increase, decrease, or stay the same? Explain. **Increase.  Because as you increase the N the standard error would decrease and the p-value would increase.**
